`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks

### 2019-09-16 analysis/paper/sim_survey_paper.Rmd
Address Greg's latest edits to the paper

---
title: "`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks"
author: "Paul M. Regular, Gregory J. Robertson, Keith P. Lewis, Jonathan Babyn, Fran Mowbray, etc.?"
date: "Fisheries and Oceans Canada, Northwest Atlantic Fisheries Center, 80 East White Hills, St. John's, Newfoundland and Labrador, A1C 5X1, Canada"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: references.bib
csl: ices-journal-of-marine-science.csl
---

@@

replot <- FALSE # plot the figures again? (acts as a manual cache)

@@

@@

This simulation framework has similarities to those presented by Schnute and Haigh [-@schnute2003] and Puerta et al. [-@puerta2019], however, efforts were focused on developing a series of general and accessible functions to simplify the process of testing multiple sampling scenarios and analytical pathways. The steps taken to simulate surveys of spatial, age-structure populations are outlined below. While the core of this paper focuses on how to use this package, it is important to note that the defaults of the package are based on a case study. Output from default function calls are therefore relavant to the case study and these results are described and discussed in [*Appendix A*][Appendix A: Case study].

@@

The **`SimSurvey`** package was written in the programming language `R` [@R] and it holds a series of functions for 1) simulating the abundance and distribution of virtural fish populations with correlation across space, time and age, 2) simulating surveys with a range of sampling stratigies and intensities, and 3) running stratified analyses of simulated survey data (Table \@ref(tab:fun)). The equations behind these functions are detailed in the sections below. **`SimSurvey`** relies heavily on functions from the **`data.table`** [@dowle2017], **`raster`** [@hijmans2016] and **`plotly`** [@sievert2018] packages for their efficient data processing, geographic and plotting facilities, respectively. Package documentation has been published online using **`pkgdown`** (https://paulregular.github.io/SimSurvey/) and all the source `R` code behind **`SimSurvey`** is available on GitHub (https://github.com/PaulRegular/SimSurvey). **`SimSurvey`** can be installed via GitHub using the **`remotes`** package:

@@

Table: (\#tab:fun) Names and descritpions of the key functions of **`SimSurvey`**. Functions in bold font are core functions and those in medium font are designed for use inside the core functions. The latter are typically closures, which are functions that contain data and return functions [@wickham2014]; here they are used to store parameter values and return functions that require dimensions, such as ages or years, to be supplied.

@@

$$N_{a,y} = N_{a-1,y-1} e^{-Z_{a-1,y-1}}$$
Here, numbers at age in the first year are filled via exponential decay, $N_{a,1} = N_{a-1,1} e^{-Z_{a-1,1}}$, numbers at age 1 (i.e. recruits) vary around a baseline value, $log(N_{1,y}) = log(\mu_r) + \epsilon_{y}$, and total mortality is set to a baseline level plus process error, $log(Z_{a,y}) = log(\mu_Z) + \delta_{a,y}$. The error around the recruitment process was set to follow a random walk, $\epsilon_{y} \sim N(\epsilon_{y - 1}, \sigma_{r}^{2})$, and the process error was simulated using the covariance structure described in Cadigan [-@Cadigan2016], $\delta_{a,y} \sim N(0, \Sigma_{a,y})$. The covariance across ages and years is controlled by a process error variance parameter ($\sigma_{\delta}^2$) along with age and year correlation parameters ($\varphi_{\delta, \mathrm{age}}$ and $\varphi_{\delta, \mathrm{year}}$, respectively). This structure allows for autocorrelation in process errors across ages and years (i.e. total mortality can be made to be more similar for fish that are closer together in age and time). Abundance at age is then converted to abundance at length using the original von Bertalanffy growth curve [@von1938]:

@@

Where $l_{\infty}$ is the mean asymptotic length, $l_0$ is length at birth, $K$ is the growth rate parameter and the error is assumed to follow the normal distribution, $\varepsilon \sim N(0, \sigma_{l}^2)$. Abundance in discrete length groups, $l_{\mathrm{group}}^{N}$, was determined by using this formula to calculate the probability of being within a specific length group given age and then using the resultant length-age-key to convert abundance at age to abundance at length. Overall, this  formulation allows for the simulation of an array of population dynamics that one might expect to observe.

Table: (\#tab:abundance) Default `sim_abundance` function call, with descriptions and associated parameter symbols of key arguments.

@@

Abundance at age and length is simulated using the `sim_abundance` function and a default function call is described in Table \@ref(tab:abundance) along with associated symbols from the equations outlined above. This function has a simple structure and requires the specification of a series of `ages` and `years` along with functions known as "closures", such as `sim_R`, `sim_Z` and `sim_vonB`, for simulating recruitment (`R`), total mortality (`Z`) and growth (`growth`), respectively. Closures are functions that contain data and return functions [@wickham2014] and this structure was chosen to avoid the repeated specifications of ages and years. The use of closures also allows users to construct and use their own closures with a similar structure but different underlying formula. Overall, the function provides a simple tool for simulating a range dynamic age-structured populations. For instance, below we provide examples where we simulate a relatively long and short lived species (note that default variance, starting abundance and growth settings were used in both simulations).

@@

The next step in the simulation is to distribute the abundance at age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ cells is generated where each cell has an area of $A$ and depth $d$; depth is defined using a sigmoid curve with a depth range of $[d_{\mathrm{min}}, d_{\mathrm{max}}]$, shelf depth of $d_{\mathrm{shelf}}$ and a shelf width of $w_{\mathrm{shelf}}$. The grid is divided into $N_{\mathrm{div}}$ divisions (e.g. NAFO or ICES divisions) and $N_{\mathrm{strat}}$ depth-based strata. The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean depth. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation within ages and years, and the two dimension AR1 age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations are controlled by a smoothing ($\lambda$) and a scaling parameter ($\kappa$) [here $\kappa$ is approximated from the range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years is controlled by $\varphi_{\xi, \mathrm{age}}$ and $\varphi_{\xi, \mathrm{year}}$, respectively. The overall variance of the process is controlled by $\sigma_{\xi}^2$ (see [*Appendix B*][Appendix B: Age-year-space covariance] for a more detailed description of the space-age-year covariance structure). In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid.

@@

| **Function call**                                       | **Description**                                              | **Symbol**                              |
|:------------------------------------------------------- |:------------------------------------------------------------ | :-------------------------------------- |
| `sim_distribution(`                                     | &nbsp;                                                       | &nbsp;                                  |
| `+  sim,`                                               | Simulated population from `sim_abundance`                    | &nbsp;                                  |
| `+  grid = make_grid(x_range = c(-140, 140),`           | Range of grid in the x dimension                             | &nbsp;                                  |
| `+                   y_range = c(-140, 140),`           | Range of grid in the y dimension                             | &nbsp;                                  |
| `+                   res = c(3.5, 3.5),`                | Grid resolution in x and y dimensions (km) - i.e. cell area  | $A_{\mathrm{cell}}$                     |
| `+                   shelf_depth = 200,`                | Shelf depth (m)                                              | $d_{\mathrm{shelf}}$                    |
| `+                   shelf_width = 100,`                | Shelf width (km)                                             | $w_{\mathrm{shelf}}$                    |
| `+                   depth_range = c(0, 1000),`         | Depth range from coast to slope (m)                          | $[d_{\mathrm{min}}, d_{\mathrm{max}}]$  |
| `+                   n_div = 1,`                        | Number of divisions                                          | $N_{\mathrm{div}}$                      |
| `+                   strat_breaks = seq(0, 1000, 40)),` | Series of depth breaks for defining strata                   | &nbsp;                                  |
| `+  ays_covar = sim_ays_covar(sd = 2.8,`                | Standard deviation of age-year-space distribution            | $\sigma_{\xi}$                          |
| `+                            range = 300,`             | Range of spatial correlation (km)                            | $r$                                     |
| `+                            lambda = 1,`              | Smoothness of spatial correlation                            | $\lambda$                               |
| `+                            phi_age = 0.5,`           | Correlation across ages in spatial distribution              | $\varphi_{\xi, \mathrm{age}}$           |
| `+                            phi_year = 0.9,`          | Correlation across years in spatial distribution             | $\varphi_{\xi, \mathrm{year}}$          |
| `+                            group_ages = 5:20),`      | Make space-age-year variance equal across these ages         | &nbsp;                                  |
| `+  depth_par = sim_parabola(mu = 200,`                 | Depth at which abundance is typically highest (m)            | $\mu_d$                                 |
| `+                           sigma = 70))`              | Dispersion around depth of peak abundance (m)                | $\sigma_d$                              |

@@

| **Function call**                   | **Description**                                                         | **Symbol**              |
|:----------------------------------- |:----------------------------------------------------------------------- | :---------------------- |
| `sim_survey(`                       | &nbsp;                                                                  | &nbsp;                  |
| `+  sim,`                           | Simulated spatial population from `sim_distribution`                    | &nbsp;                  |
| `+  n_sims = 1`                     | Number of times to repeat the survey                                    | &nbsp;                  |
| `+  q = sim_logistic(k = 2,`        | Steepness of logistic curve of catchability                             | $k$                     |
| `+                   x0 = 3),`      | Midpoint of logistic curve of catchability                              | $x_0$                   |
| `+  trawl_dim = c(1.5, 0.02),`      | Trawl dimensions (length, width; km) - i.e. area covered by a trawl     | $A_{\mathrm{trawl}}$    |
| `+  min_sets = 2`                   | Minimum number of sets to conduct per strata                            | &nbsp;                  |
| `+  set_den = 2/1000,`              | Set density (km^-2^)                                                    | $D_{\mathrm{sets}}$     |
| `+  lengths_cap = 500,`             | Maximum number of lengths to collect / set                              | $M_{\mathrm{lengths}}$  |
| `+  length_group = 1,`              | Length group bin size for age sampling (cm)                             | $l_{\mathrm{group}}$    |
| `+  ages_cap = 10,`                 | Maximum number of ages to sample / length group / division              | $M_{\mathrm{ages}}$     |
| `+  age_sammpling = "stratified")`  | Controls whether age sampling is length `"stratified"` or `"random"`    | &nbsp;                  |

@@

p <- facet_fan(tests, lengths = 1:100, ylim = c(0, 21000000)) %>% 
  layout(margin = list(r = 30)) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", c(0.0005, 0.002, 0.01))) %>% 
  add_labels(x = rep(1, 3), y = c(0.05, 0.5, 0.95), xshift = 30, textangle = 90,
             text = paste("M<sub>lengths</sub> =", rev(c(10, 100, 1000)))) %>% 
  add_labels(x = 0.5, y = 0, text = "Year", yshift = -40) %>% 
  add_labels(x = 0, y = 0.5, text = "Abundance index", xshift = -60, textangle = -90)

@@

p <- facet_fan(tests, ages = 1:10, ylim = c(0, 51000000)) %>% 
  layout(margin = list(r = 30)) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", c(0.0005, 0.002, 0.01))) %>% 
  add_labels(x = rep(1, 3), y = c(0.05, 0.5, 0.95), xshift = 30, textangle = 90,
             text = paste("M<sub>age</sub> =", rev(c(10, 100, 1000)))) %>% 
  add_labels(x = 0.5, y = 0, text = "Year", yshift = -40) %>% 
  add_labels(x = 0, y = 0.5, text = "Abundance index", xshift = -60, textangle = -90)

@@

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell, instead fish may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. These assumptions, plus a range of others, will surely under-represent the natural variability of fish populations and survey protocol. Nevertheless, the **`SimSurvey`** package provides the most realistic operating model that we are aware of for simulating stratified-random survey data from a population that varies across age, year and space dimensions.

<!-- # Should we include a summary of the case study - previous abstrat included below -->

<!-- A central question to fish stock assessments is: how many samples are needed to adequately represent the population being monitored? For assessments based on trawl surveys, our ability to estimate population characteristics, such as abundance at age, is affected by multiple levels of sampling (i.e. the number of sets, lengths and ages sampled in a survey). We therefore need to assess the impact of haul design and length and age sampling on survey accuracy to determine optimal sampling effort. In this study we simulated repeated stratified-random samples from a spatially correlated field of simulated fish. These samples were then analyzed and estimates of abundance at age were compared against a known truth. By varying the sampling protocol, we demonstrate that increasing the number of sets conducted per stratum provides the greatest gains in precision when sampling a clustered population. Increasing length and age sampling efforts also improved abundance estimates, but to a lesser extent and improvements were typically marginal, and sometimes squandered, when sub-sampling effort was increased. These results indicate that high levels of length and age sampling effort can be scaled back without significant losses to precision and, in some cases, estimates of abundance at age may be improved by reducing sub-sampling effort. Time saved by reducing said sampling may afford more time to conduct additional sets and/or increase sampling efforts of other species. While this simulation is tailored to a specific case, the method may be adapted to different systems and survey procedures. -->

@@

The case study described in [*Appendix A*][Appendix A: Case study] provides one example of ways in which **`SimSurvey`** can be used to simulation test the design of fisheries-independent trawl surveys. There are multiple layers to the sampling design of such surveys and the end results are linked with the way such data are analyzed. Below we outline some examples where the **`SimSurvey`** package may aid future research efforts.

@@

The **`SimSurvey`** package serves as a tool for simulating stratified random surveys of dynamic populations that vary across ages, time and space. The core of the simulation is based on the widely used cohort equation and, even though the processes that define recruitment and total mortality are simple, a wide range of stock dynamics can be simulated by changing a few parameters. This base population can then be distributed through a grid and relationships with depth can be defined as can the nature of the correlation across ages, years and space. Together, two functions (`sim_abundance` and `sim_distribution`) are capable of simulating a wide range of populations with different life histories, depth associations and spatial properties. The next necessary steps to generating data similar to actual observations is to conduct a survey. In this package we implement a function, `sim_survey`, that conducts a stratified random survey of the population. The sampling process is governed by the area covered by the trawl as well as age-specific catchability. Sub-sampling protocol (length and age sampling) can also be varied. As such, data from a wide range of surveys can be simulated.

@@

>>>>

---
title: "`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks"
author: "Paul M. Regular, Gregory J. Robertson, Keith P. Lewis, Jonathan Babyn, Fran Mowbray"
date: "Fisheries and Oceans Canada, Northwest Atlantic Fisheries Center, 80 East White Hills, St. John's, Newfoundland and Labrador, A1C 5X1, Canada"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: references.bib
csl: ices-journal-of-marine-science.csl
---

@@

replot <- TRUE # plot the figures again? (acts as a manual cache)

@@

# Things to manually fix in word

1. Adjust font size of code strings
2. Decrease font size of tables
3. Indent closures in Table \@ref(tab:fun)
4. Replace pluses (`+`) with spaces in Tables \@ref(tab:abundance) to (\#tab:survey)
1. Remove this section

@@

This simulation framework has similarities to those presented by Schnute and Haigh [-@schnute2003] and Puerta et al. [-@puerta2019], however, efforts were focused on developing a series of general and accessible functions to simplify the process of testing multiple sampling scenarios and analytical pathways. The steps taken to simulate surveys of spatial, age-structure populations are outlined below. While the core of this paper focuses on how to use this package, it is important to note that the defaults of the package are based on a case study. Output from default function calls are therefore relevant to the case study and these results are described and discussed in [*Appendix A*][Appendix A: Case study].

@@

The **`SimSurvey`** package was written in the programming language `R` [@R] and it holds a series of functions for 1) simulating the abundance and distribution of virtual fish populations with correlation across space, time and age, 2) simulating surveys with a range of sampling strategies and intensities, and 3) running stratified analyses of simulated survey data (Table \@ref(tab:fun)). The equations behind these functions are detailed in the sections below. **`SimSurvey`** relies heavily on functions from the **`data.table`** [@dowle2017], **`raster`** [@hijmans2016] and **`plotly`** [@sievert2018] packages for their efficient data processing, geographic and plotting facilities, respectively. Package documentation has been published online using **`pkgdown`** (https://paulregular.github.io/SimSurvey/) and all the source `R` code behind **`SimSurvey`** is available on GitHub (https://github.com/PaulRegular/SimSurvey). **`SimSurvey`** can be installed via GitHub using the **`remotes`** package:

@@

Table: (\#tab:fun) Names and descriptions of the key functions of **`SimSurvey`**. Functions in bold font are core functions and those in medium font are designed for use inside the core functions. The latter are typically closures, which are functions that contain data and return functions [@wickham2014]; here they are used to store parameter values and return functions that require dimensions, such as ages or years, to be supplied.

@@

$$N_{a,y} = N_{a-1,y-1} e^{-Z_{a-1,y-1}}$$
Here, numbers at age in the first year are filled via exponential decay, $N_{a,1} = N_{a-1,1} e^{-Z_{a-1,1}}$, numbers at age 1 (i.e. recruits) vary around a baseline value, $log(N_{1,y}) = log(\mu_r) + \epsilon_{y}$, and total mortality is set to a baseline level plus process error, $log(Z_{a,y}) = log(\mu_Z) + \delta_{a,y}$. The error around the recruitment process was set to follow a random walk, $\epsilon_{y} \sim N(\epsilon_{y - 1}, \sigma_{r}^{2})$, and the process error was simulated using the covariance structure described in Cadigan [-@Cadigan2016], $\delta_{a,y} \sim N(0, \Sigma_{a,y})$. The covariance across ages and years is controlled by a process error variance parameter ($\sigma_{\delta}^2$) along with age and year correlation parameters ($\varphi_{\delta, \mathrm{age}}$ and $\varphi_{\delta, \mathrm{year}}$, respectively). This structure allows for autocorrelation in process errors across ages and years (i.e. total mortality can be made to be more similar for fish that are closer together in age and/or time). Abundance at age is then converted to abundance at length using the original von Bertalanffy growth curve [@von1938]:

@@

Where $l_{\infty}$ is the mean asymptotic length, $l_0$ is length at birth, $K$ is the growth rate parameter and the error is assumed to follow the normal distribution, $\varepsilon \sim N(0, \sigma_{l}^2)$. Abundance in discrete length groups, $l_{\mathrm{group}}^{N}$, was determined by using this formula to calculate the probability of being within a specific length group given age and then using the resultant length-age-key to convert abundance at age to abundance at length. Though some typical relationships have yet to be implemented (e.g. stock-recruitment), this formulation facilitates the simulation of age-structured populations that are dynamic enough to test an array of survey designs.

Table: (\#tab:abundance) Default `sim_abundance` function call, with descriptions, default values and associated parameter symbols of key arguments.

@@

Abundance at age and length is simulated using the `sim_abundance` function and a default function call is described in Table \@ref(tab:abundance) along with associated symbols from the equations outlined above. This function has a simple structure and requires the specification of a series of `ages` and `years` along with functions known as "closures", such as `sim_R`, `sim_Z` and `sim_vonB`, for simulating recruitment (`R`), total mortality (`Z`) and growth (`growth`), respectively. Closures are functions that contain data and return functions [@wickham2014]. For example, `sim_R(mean = 500, log_sd = 0.5)` returns a function that holds the supplied parameter values and requires a sequence of years to be supplied. (Note that each of the above-mentioned closures include a plot argument such that quick visuals can be obtained using a line of code like this: `sim_R(mean = 500, log_sd = 0.5, plot = TRUE)(years = 1:100)`). This structure was chosen to avoid the repeated specifications of ages and years. The use of closures also allows users to construct and use their own closures with a similar structure but different underlying formula. Overall, the function provides a simple tool for simulating a range of dynamic age-structured populations. For instance, below we provide examples where we simulate a relatively long and short lived species (note that default variance, starting abundance and growth settings were used in both simulations).

@@

The next step in the simulation is to distribute the abundance at age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ cells is generated where each cell has an area of $A$ and depth $d$; depth is defined using a sigmoid curve with a depth range of $[d_{\mathrm{min}}, d_{\mathrm{max}}]$, shelf depth of $d_{\mathrm{shelf}}$ and a shelf width of $w_{\mathrm{shelf}}$. The grid is divided into $L_{\mathrm{div}}$ divisions (e.g. NAFO or ICES divisions) and $L_{\mathrm{strat}}$ depth-based strata. The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean depth. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation within ages and years, and a two dimension AR1 age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations are controlled by a smoothing ($\lambda$) and a scaling parameter ($\kappa$) [here $\kappa$ is approximated from the range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years is controlled by $\varphi_{\xi, \mathrm{age}}$ and $\varphi_{\xi, \mathrm{year}}$, respectively. The overall variance of the spatial process is controlled by $\sigma_{\xi}^2$ (see [*Appendix B*][Appendix B: Age-year-space covariance] for a more detailed description of the space-age-year covariance structure). In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid.

@@

| **Function call**                                       | **Description**                                              | **Symbol**                              |
|:------------------------------------------------------- |:------------------------------------------------------------ | :-------------------------------------- |
| `sim_distribution(`                                     | &nbsp;                                                       | &nbsp;                                  |
| `+  sim,`                                               | Simulated population from `sim_abundance`                    | &nbsp;                                  |
| `+  grid = make_grid(x_range = c(-140, 140),`           | Range of grid in the x dimension                             | &nbsp;                                  |
| `+                   y_range = c(-140, 140),`           | Range of grid in the y dimension                             | &nbsp;                                  |
| `+                   res = c(3.5, 3.5),`                | Grid resolution in x and y dimensions (km) - i.e. cell area  | $A_{\mathrm{cell}}$                     |
| `+                   shelf_depth = 200,`                | Shelf depth (m)                                              | $d_{\mathrm{shelf}}$                    |
| `+                   shelf_width = 100,`                | Shelf width (km)                                             | $w_{\mathrm{shelf}}$                    |
| `+                   depth_range = c(0, 1000),`         | Depth range from coast to slope (m)                          | $[d_{\mathrm{min}}, d_{\mathrm{max}}]$  |
| `+                   n_div = 1,`                        | Number of divisions                                          | $L_{\mathrm{div}}$                      |
| `+                   strat_splits = 2,                  | Number of times to horizontally split strat                  | &nbsp;                                  |
| `+                   strat_breaks = seq(0, 1000, 40)),` | Series of depth breaks for defining strata                   | &nbsp;                                  |
| `+  ays_covar = sim_ays_covar(sd = 2.8,`                | Standard deviation of age-year-space distribution            | $\sigma_{\xi}$                          |
| `+                            range = 300,`             | Range of spatial correlation (km)                            | $r$                                     |
| `+                            lambda = 1,`              | Smoothness of spatial correlation                            | $\lambda$                               |
| `+                            phi_age = 0.5,`           | Correlation across ages in spatial distribution              | $\varphi_{\xi, \mathrm{age}}$           |
| `+                            phi_year = 0.9,`          | Correlation across years in spatial distribution             | $\varphi_{\xi, \mathrm{year}}$          |
| `+                            group_ages = 5:20),`      | Make space-age-year variance equal across these ages         | &nbsp;                                  |
| `+  depth_par = sim_parabola(mu = 200,`                 | Depth at which abundance is typically highest (m)            | $\mu_d$                                 |
| `+                           sigma = 70))`              | Dispersion around depth of peak abundance (m)                | $\sigma_d$                              |

@@

| **Function call**                   | **Description**                                                         | **Symbol**              |
|:----------------------------------- |:----------------------------------------------------------------------- | :---------------------- |
| `sim_survey(`                       | &nbsp;                                                                  | &nbsp;                  |
| `+  sim,`                           | Simulated spatial population from `sim_distribution`                    | &nbsp;                  |
| `+  n_sims = 1`                     | Number of times to repeat the survey                                    | &nbsp;                  |
| `+  q = sim_logistic(k = 2,`        | Steepness of logistic curve of catchability                             | $k$                     |
| `+                   x0 = 3),`      | Midpoint of logistic curve of catchability (age)                        | $x_0$                   |
| `+  trawl_dim = c(1.5, 0.02),`      | Trawl dimensions (length, width; km) - i.e. area covered by a trawl     | $A_{\mathrm{trawl}}$    |
| `+  min_sets = 2`                   | Minimum number of sets to conduct per strata                            | &nbsp;                  |
| `+  set_den = 2/1000,`              | Set density (km^-2^)                                                    | $D_{\mathrm{sets}}$     |
| `+  lengths_cap = 500,`             | Maximum number of lengths to collect / set                              | $M_{\mathrm{lengths}}$  |
| `+  length_group = 1,`              | Length group bin size for age sampling (cm)                             | $l_{\mathrm{group}}$    |
| `+  ages_cap = 10,`                 | Maximum number of ages to sample / length group / division              | $M_{\mathrm{ages}}$     |
| `+  age_sammpling = "stratified")`  | Controls whether age sampling is length `"stratified"` or `"random"`    | &nbsp;                  |

@@

p <- facet_fan(tests, lengths = 1:100, ylim = c(0, 21000000)) %>% 
  layout(margin = list(r = 30)) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", c(0.0005, 0.002, 0.01))) %>% 
  add_labels(x = rep(1, 3), y = c(0.05, 0.5, 0.95), xshift = 30, textangle = 90,
             text = paste("M<sub>lengths</sub> =", rev(c(10, 100, 1000)))) %>% 
  add_labels(x = 0.5, y = 0, text = "Length", yshift = -40) %>% 
  add_labels(x = 0, y = 0.5, text = "Abundance index", xshift = -60, textangle = -90)

@@

p <- facet_fan(tests, ages = 1:10, ylim = c(0, 51000000)) %>% 
  layout(margin = list(r = 30)) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", c(0.0005, 0.002, 0.01))) %>% 
  add_labels(x = rep(1, 3), y = c(0.05, 0.5, 0.95), xshift = 30, textangle = 90,
             text = paste("M<sub>length</sub> =", rev(c(10, 100, 1000)))) %>% 
  add_labels(x = 0.5, y = 0, text = "Age", yshift = -40) %>% 
  add_labels(x = 0, y = 0.5, text = "Abundance index", xshift = -60, textangle = -90)

@@

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell, instead fish may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. These assumptions, plus a range of others, will surely under-represent the natural variability of fish populations and survey protocol. Nevertheless, the **`SimSurvey`** package provides a relatively complex and flexible operating model for simulating stratified-random survey data from a population that varies across age, year and space dimensions.

@@

The case study described in [*Appendix A*][Appendix A: Case study] provides one example of how **`SimSurvey`** can be used to simulation test the design of fisheries-independent trawl surveys. There are multiple layers to the sampling design of such surveys and the end results are linked with the way such data are analyzed. Below we outline some examples where the **`SimSurvey`** package may aid future research efforts.

@@

The **`SimSurvey`** package serves as a tool for simulating stratified random surveys of dynamic populations that vary across ages, time and space. The core of the simulation is based on the widely used cohort equation and, even though the processes that define recruitment and total mortality are simple, a wide range of stock dynamics can be simulated by changing a few parameters. This base population can then be distributed through a grid and relationships with depth and correlation across ages, years and space can be defined. Together, two functions (`sim_abundance` and `sim_distribution`) are capable of simulating a wide range of populations with different life histories, depth associations and spatial properties. The next necessary steps to generating data similar to actual observations is to conduct a survey. In this package we implement a function, `sim_survey`, that conducts a stratified random survey of the population. The sampling process is governed by the area covered by the trawl as well as age-specific catchability. Sub-sampling protocol (length and age sampling) can also be varied. As such, data from a wide range of surveys can be simulated.

@@

# install.packages("remotes")
# remotes::install_github("PaulRegular/SimSurvey")
# library(SimSurvey)
